---
title: "36-315 Static Graphics Project"
author: "Andrew Lee, Weng Shian Ho, Daniel Liu, Yeju Ahn"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

+  A link to the dataset:
[here](https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016)

+   Description of the dataset: 
This dataset was built to find signals correlated to increased suicide rates among different cohorts globally, across the socio-economic spectrum.

Variables include:
+   Country
+   Year
+   Sex
+   Age
+   Suicides No
+   Population
+   Suicides/100k pop
+   Country Year
+   HDI for year (Human Development Index)
+   gdp_for_year ($)
+   gdp_per_capita ($)
+   generation

*CSV FILE*
```{r}
library(tidyverse)
library(car)
suicide_data <- read.csv("suicide-dataset.csv")
dim(suicide_data)
nrow(suicide_data)
ncol(suicide_data)
colnames(suicide_data)
is.factor(suicide_data$country)
is.factor(suicide_data$sex)
is.factor(suicide_data$generation)
```

```{r,warning = FALSE,message = FALSE}
library(igraph)
library(igraphdata)
library(dendextend)
countries <- map_data("world2")
country_list <- unique(suicide_data$country)
country_cords <- data.frame()
for (i in 1:length(country_list)){
  curr.country <- country_list[i]
  curr.country.data <- countries[which(countries$region == curr.country),]
  curr.avg.lat <- mean(curr.country.data$lat)
  curr.avg.long <- mean(curr.country.data$long)
  curr.avg.grp <- round(median(curr.country.data$group))
  curr.dist <- data.frame(Country = curr.country, Lat = curr.avg.lat, long =  curr.avg.long, group = curr.avg.grp)
  country_cords <- rbind(country_cords, curr.dist)
}

suicides.2015 <- suicide_data[which(suicide_data$year == 2015),]
country_list <- unique(suicides.2015$country)
country.suicides.2015 <- data.frame()

for (i in 1:length(country_list)){
  curr.country <- country_list[i]
  curr.avg.gdp <- mean(curr.country.data$gdp_per_capita....)
  curr.country.data <- suicides.2015[which(suicides.2015$country == curr.country),]
  curr.suicide.rate <-  sum(curr.country.data$suicides_no/curr.country.data$population)
  curr.data.frame <- data.frame(Country = curr.country, Rate = curr.suicide.rate)
  country.suicides.2015 <- rbind(country.suicides.2015,curr.data.frame)
}
all.suicides.2015.data <- merge(country.suicides.2015,country_cords, by = intersect("Country", "Country"))

mod_2015 <- ggplot(suicides.2015, aes(x =gdp_per_capita....,y = suicides_no, label = country)) + geom_text(check_overlap = TRUE,aes(color = population)) +
  labs(title = "GDP Per Capita in 2015 ",x =  "GDP Per Capita", y = "Suicides No.")
mod_2015
```


```{r}
mod_1990 <- suicides.1990 <- suicide_data[which(suicide_data$year == 1990),]
ggplot(suicides.1990, aes(x =gdp_per_capita....,y = suicides_no, label = country)) + geom_text(check_overlap = TRUE,aes(color = population)) +
  labs(title = "GDP Per Capita in 1990",x =  "GDP Per Capita", y = "Suicides No.")
```


```{r}
suicide_data <- suicide_data %>% filter(year %in% c("1990","  ","2015"))
ggplot(suicide_data, aes(x =gdp_per_capita....,y = suicides_no, label = country)) + geom_text(check_overlap = TRUE,aes(color = population, size= factor(year))) +
  labs(title = "GDP Per Capita of countries in 1990 and 2015",x =  "GDP Per Capita", y = "Suicides No.", size = "Year")
```



```{r}
Pclass_dist_plot <- ggplot(data = suicide_data, aes(x = generation))

Pclass_dist_plot + geom_bar(aes(x = factor(1),fill = generation)) + coord_polar(theta = "y") +labs(
 title = "Suicide Deaths by Generation", x = "", y = "")+  theme(
        axis.text.y = element_blank(),axis.ticks.y = element_blank())
```

