---
title: "36-315 Static Graphics Project"
author: "Andrew Lee, Weng Shian Ho, Daniel Liu, Yeju Ahn"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  hide
---

+  A link to the dataset:
[here](https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016)

+   Description of the dataset: 
This dataset was built to find signals correlated to increased suicide rates among different cohorts globally, across the socio-economic spectrum.

Variables include:
+   Country
+   Year
+   Sex
+   Age
+   Suicides No
+   Population
+   Suicides/100k pop
+   Country Year
+   HDI for year (Human Development Index)
+   gdp_for_year ($)
+   gdp_per_capita ($)
+   generation

*CSV FILE*
```{r}
library(tidyverse)
library(car)
suicide_data <- read.csv("suicide-dataset.csv")
dim(suicide_data)
nrow(suicide_data)
ncol(suicide_data)
colnames(suicide_data)
is.factor(suicide_data$country)
is.factor(suicide_data$sex)
is.factor(suicide_data$generation)
```

#Multiple Linear Regression Analysis

Suicides/100k pop x Year  : Not significant
```{r}
suicide_year_mod <- lm(suicides_no ~ year , data = suicide_data)
summary(suicide_year_mod)
```

Suicides/100k pop x Sex  : Significance
```{r}
suicide_sex_mod <- lm(suicides_no ~ sex, data = suicide_data)
summary(suicide_sex_mod)
```

Suicides/100k pop x Country  : Significance
```{r}
suicide_country_mod <- lm(suicides_no ~ country, data = suicide_data)
summary(suicide_country_mod)
```

Suicides/100k pop x Age : Significance
```{r}
suicide_age_mod <- lm(suicides_no ~ age, data = suicide_data)
summary(suicide_age_mod)
```

Suicides/100k pop x GDP_per_capita : Significance
```{r}
suicide_gdp_mod <- lm(suicides_no ~ gdp_per_capita...., data = suicide_data)
summary(suicide_gdp_mod)
```

Suicides/100k pop x Generation : Significance
```{r}
suicide_gen_mod <- lm(suicides_no ~ generation, data = suicide_data)
summary(suicide_gen_mod)
```

Suicides/100k pop x HDI : Significance
```{r}
suicide_HDI_mod <- lm(suicides_no ~ HDI.for.year, data = suicide_data)
summary(suicide_HDI_mod)
```
```{r}
fit <- lm(suicides_no~sex+country+gdp_per_capita....+generation+HDI.for.year, data=suicide_data)
summary(fit)
```

```{r fig.width=4, fig.width=5.5, fig.align="center",echo = FALSE}
resid_new <- fit$residuals
pred.vals_new <- fit$fitted.values
plot(resid_new~pred.vals_new,
     main = "Residuals vs Fitted", 
     xlab = "Fitted values", 
     ylab = "Residuals")
abline(h=0)
```

```{r, fig.height=4, fig.width=5, echo=FALSE}
qqnorm(resid_new,
       main="Normal probability plot for residuals") 
qqline(resid_new)
```


```{r}
vif(fit) # variance inflation factors 
```


#Times Series Plot




